Qualifying Examination Paper

### 2018-11-14 main.tex
181114-0632 sync

\paragraph{Evidence Assumptions:}
\begin{enumerate}
    \item The distribution for $I$ is equivalent to the distribution upon which the scene estimator providing $p(S_n = s \mid I_n)$ was trained.
    \item The distribution for $I$ is equivalent to the distribution upon which the object estimator providing $p(I_n \mid i_{nm} \textrm{ on } o)$ was trained.
    \item Both tasks are semi-supervised, such that the only form of labeled data is $t_n$\footnote{The semi-supervised assumption was adopted because human point-and-click labeling of private image regions for both training and updating of models is thought to be a realistic scenario.}.  Note that this assumption implies that $t_n$ will not be available at test time.
\end{enumerate}

@@

The objective for this task can be stated as estimating $\{\forall m \in \lbrack0,M), P(C_{P_{m}} = 1 \mid I, \textrm{ evidence}) \}$ where $C_{P_m}$ is the binary class label for whether a pixel $i_m$ is part of a benign object/region (0) or part of a private object/region (1).  This set or probabilities can be regarded as a `privacy map' of $I$ for use in sensorship, for example.

@@

To form the basis of the probabilistic model, a belief network which juxtaposes our evidence and other random variables into the believed set of dependency assumptions can be created. The dependency assumptions are defined as follows.  Firstly, an image ($I$) is the result of, and therefore depends on, the true object-to-pixel mapping ($i_m$ on $o_k$) that is captured by the camera.  Secondly, the scene type ($S$) prediction is based on, and therefore depends on, the image ($I$).  Thirdly, whether or not the object $o_k$ is private is dependent on $t$, but since $t$ is not available at test time $o_k$'s privacy will be regarded as independent from any observable variable.  Lastly, we'll assume for now that image metadata ($D$) in its raw form doesn't meaningfully contribute to the privacy determination problem.  GPS location and time stamps may be useful for influencing the scene probabilities or accounting for lighting differences in the image for object recognition, but we do not have direct influence over those predictors.  The resulting belief network is shown in Figure \ref{fig:belief}.

\begin{figure}[ht]
\centering
    \begin{tikzpicture}[
        every node/.style={shape=ellipse, draw}
    ]
    %NODES
    %\node (mt) {$m \in t$};
    \node (io) {$i_{m}\textrm{ on }o_k$};
    \node (i)  [right = of io] {$I$};
    \node (s) [right = of i] {$S$};
    %\node (t) [below = of po, text width=2cm, align=center] {$i_m \textrm{ on } o_k, \exists i_l \textrm{ on } o_k$ s.t. $l \in t$};
    %\node (op) [below = of io] {$\exists i_l \textrm{ on } o_k \textrm{ s.t. } l \in t$};
    \node (or) [below = of i] {$o_k$ is private};
    \node (d) [right = of s] {$D$};

    %PATHS
    \path   (io) edge [->] (i);
    \path   (i) edge [->] (s);
    %\path   (po) edge [->] (t);
    %\path   (po) edge [->] node [left, draw=none] {$f_t$} (t);
    %\path   (or) edge [->] (op);
    \end{tikzpicture}
    \caption{Belief Network}\label{fig:belief}
    %\medskip
    %\small
\end{figure}

Now we are ready to perform some Bayesian inference to obtain $p(i_m \textrm{ on } o, o \textrm{ is private} \mid I, \textrm{ evidence})$.

@@

Time complexity for all algorithms are given in their respective captions.  $N$ is number of images, $M$ is number of pixels per image, $K$ is number of object types, $L_n$ is number of objects in image $I_n$, $Q$ is the number of neighbors to pixels, and $T$ is number of iterations (for root finding).

Equation \ref{eqn:indep} illustrates independence of the events that a specific pixel belongs to a specific object and that object being a private object type.  However, the prior distribution $p(i_m \textrm{ on } o \mid I)$ is still unknown.  We will consider the factors in Equation \ref{eqn:joint} to estimate it.  Estimation of $p(i_m \textrm{ on } o \mid I)$ can be regarded as a constrained Maximum a Priori (MAP) estimation follows:

\begin{gather}
	\theta : \Big(p(i_m \textrm{ on } o_0), p(i_m \textrm{ on } o_1),
		\dots, p(i_m \textrm{ on } o_K)\Big) \\
	L(\theta) = \prod_{n=0}^{N} \sum_{k=0}^{K} p(I_n \mid i_{nm} 
		\textrm{ on } o_k) \theta_k \\
	LL(\theta) = \sum_{n=0}^{N} \log \Big( \sum_{k=0}^{K} 
		p(I_n \mid i_{nm} \textrm{ on } o_k) \theta_k \Big) \label{eqn:loglik}\\
	\sum_{k=0}^{K} \theta_k - 1 = 0 \label{eqn:constr}\\
	\mathcal{L}(\theta, \lambda) = \sum_{n=0}^{N} \log 
		\Big( \sum_{k=0}^{K} p(I_n \mid i_{nm} \textrm{ on } o_k) \theta_k \Big) + \lambda - \lambda \sum_{k=0}^{K} \theta_k \label{eqn:lagr}\\
	\mathbf{F}^{K \times 1}: \mathbf{F}_k = \frac{\partial \mathcal{L}}{\partial \theta_k} = 
		\sum_{n=0}^{N} \frac
			{p(I_n \mid i_{nm \textrm{ on } o_k})}
			{\sum_{j=0}^{K} p(I_n \mid i_{nm \textrm{ on } o_j}) \theta_j} = 0;
		\frac{\partial \mathcal{L}}{\partial \lambda} = 1 - \sum_{k=0}^{K} 
			\theta_k = 0 \label{eqn:lagr1der}\\
	\mathbf{J}^{K \times K}: \mathbf{J}_{i,j} = \frac{\partial}{\partial \theta_j} \left( \frac
		{\partial \mathcal{L}}{\partial \theta_i} \right) = 
		\sum_{n=0}^{N} \frac
			{-p(I_n \mid i_{nm \textrm{ on } o_i})p(I_n \mid i_{nm \textrm{ on } o_j})}
			{(\sum_{l=0}^{K} p(I_n \mid i_{nm \textrm{ on } o_l}) \theta_l)^2} \label{eqn:lagr2der};
		\frac{\partial}{\partial \lambda} \left( \frac{\partial \mathcal{L}}{\partial \lambda} \right) = 0
\end{gather}

Equation \ref{eqn:loglik} represents the Log Likelihood of the observed data to be maximized over $\theta$, and Equation \ref{eqn:constr} represents the constraint that prior probabilities for all object types sum to 1.  A Lagrangian (Equation \ref{eqn:lagr}) is constructed to define the boundary on the Log Likelihood along which the constraint is satisfied.  The roots of the vector of first derivatives for this boundary (Equation \ref{eqn:lagr1der}) will contain the prior distribution that maximizes the posterior distribution.  Equation \ref{eqn:lagr1der} is difficult to solve in closed form. Thus, we will use the Newton-Raphson root finding algorithm to estimate the roots in quadratic time, Algorithm \ref{alg:newtraph}.  This algorithm also requires the second derivative of the Lagrangian, a Jacobian matrix, expressed in Equation \ref{eqn:lagr2der}.

\begin{algorithm}[h!]\label{alg:newtraph}
\caption{Newton-Raphson Root Finding Algorithm, $O(M(NK + K^3 + TNK))$}
	\KwData{
		$X \leftarrow p(I_n \mid i_{nm} \textrm{ on } o_k)$}
	\KwResult{$\theta^{M \times K}: \{\vec{\theta}_{0}^K, \dots, \vec{\theta}_{M}^K\}$}
	$\theta \leftarrow 0^{M \times K}$\;
	$\alpha \leftarrow$ small constant; $T \leftarrow$ small constant\;
	\For{$m \leftarrow 0$ \KwTo $M$}{
		\For{$n \leftarrow 0$ \KwTo $N$}{
			$\vec{\theta_{m}} \leftarrow \vec{\theta_{m}} + 
				\frac{\vec{p(I_n \mid i_{nm} \textrm{ on } o)}}{N \times \sum_{k=0}^{K} p(I_n \mid i_{nm} \textrm{ on } o_k)}$
				// initial guess for $\theta_{m}$ assuming $I$ is uniform\;
		}
		Build $\mathbf{F}$ // Equation \ref{eqn:lagr1der} complexity $O(NK)$\;
		Build $\mathbf{J}^{-1}$ // Inverse matrix of Equation \ref{eqn:lagr2der} complexity $O(NK+K^3)$\;
		$t \leftarrow 0$\;
		\While{$\mathbf{F}(\theta_{m}) > \alpha$ and $t < T$}{
			$\vec{\theta_m} \leftarrow \vec{\theta_m} - 
				\mathbf{J}(\vec{\theta_m})^{-1} \mathbf{F}(\vec{\theta_m})$
				// complexity $O(NK)$\;
			$t \leftarrow t + 1$\;
		}
	$\vec{\theta_m} \leftarrow \vec{\theta_m} / sum_{k=0}^{K} \theta_{mk}$
		// satisfy constraint (i.e. solve for $\lambda$)\;
	}
\end{algorithm}

@@

However, $p(i_m \textrm{ on } o \mid I)$ is still based on noisy evidence, which has a high potential for resulting in a falsely high number of contiguous object regions.  Aside from the affect of identifying only small portions of private objects, this will also adversely affect $p(o_k \textrm{ is priv})$ by driving up the number of unmarked private objects and potentially mislabeling those that are marked.  Efficient belief propagation over pixels arranged as Markov Random Fields (MRF) has been shown to produce good results in scenarios where labels are unlikely to change between two neighboring pixels except in border regions \cite{felzenszwalb2006efficient}.  We use a variant of this approach to help regularize the noisy $p(i_m \textrm{ on } o \mid I)$ evidence to achieve $p_R(i_m \textrm{ on } o \mid I)$, as shown in Algorithm \ref{alg:regObjMap}.

\begin{algorithm}[h!]\label{alg:regObjMap}
\caption{Regularize the Object Map, $O(NTMQ^2K)$}
\KwData{
    $I: \lbrack 0,256 \rbrack^{M \times H} \rightarrow \{i_{mh} \mid \forall m \in \lbrack 0, M ), \forall h \in \lbrack 0, H)\}$}
\KwResult{$p_R(i_m \textrm{ on } o \mid I)$}
$T \leftarrow$ small number // number of iterations for message updates\;
$d \leftarrow$ small positive constant // penalty for labeling variation\;
$D^{M \times K} \leftarrow -log(p(i_m \textrm{ on } o \mid I))$ /* get object probability map from noisy evidence and convert values to negative log */\;
MSG$^t \leftarrow 0^{M \times \lvert m\textrm{'s neighbors} \rvert \times K}$\;
MSG$^{t-1}$\;
PMAP $\leftarrow$ null$^{M \times K}$\;
\SetKwFunction{h}{h}
\SetKwProg{Def}{def}{:}{}
\Def{\h{x: coord}}{
    res $\leftarrow 0^K$\;
    \For{$k \leftarrow 0$ \KwTo $K$}{
        \For{$q \in$ Neighbors($x$)}{
            $res_k \leftarrow res_k +$ MSG$^{t-1}_{q,x,k}$\;
        }
        $res_k \leftarrow res_k + D_{x,k}$\;
    }
    return $res$
}
\SetKwFunction{Nei}{Neighbors}
\Def{\Nei{x}}{return 8 pixel coordinates around x // could be 4\;}
\For{$t \leftarrow 0$ \KwTo $T$}{
    // Update messages $T$ times\;
    MSG$^{t-1} \leftarrow$ MSG$^t$\;
    \For{$m \leftarrow 0$ \KwTo $M$}{
        // for each pixel coordinate\;
        $h_m \leftarrow$ \h{$m$}\;
        $h_{m_{min}} \leftarrow \min_{k} (h_m + d)$\;
        $Q \leftarrow$ Neighbors($m$)\;
        \For{$q \in Q$}{
            $h_q \leftarrow$ \h{$q$}\;
            \For{$k \leftarrow 0$ \KwTo $K$}{
                MSG$^t_{m,q,k} \leftarrow \min (h_{q_{k}}, h_{m_{min}})$
            }
        }
    }
}
\For{$m \leftarrow 0$ \KwTo $M$}{
    $p_R(i_m \textrm{ on } o \mid I) \leftarrow \frac
	    {\vec{log^{-1}(-\textrm{\h{m}})}}
	    {\sum_{k=0}^{K}log^{-1}(-\textrm{\h{m}})}$
	    // conv. to probability and ensure normalized\;
}
return res\;
\end{algorithm}

The final task is to estimate $p(o \textrm{ is priv})$.  To achieve this, we need to enumerate all the object instances, their types, their respective probabilities, and whether they are private.  To achieve this, we us a variant of the Two-Pass Connected Component Labeling algorithm \cite{hoshen1976percolation}, described in Algorithm \ref{alg:objEnum}.  It is important to note that although objects are enumerated according to the high object type probabilities for each pixel, probability summations for all objects types are preserved at each pixel.  This will be important later.

\begin{algorithm}[h!]\label{alg:objEnum}
\caption{Object Enumeration, $O(NMQ + L)$}
	\KwData{$P^{N \times M \times K} \leftarrow p_R(i_{nm} \textrm{ on } o_k \mid I_n) \forall n \in \lbrack 0,N), \forall m \in \lbrack0,M), \forall k \in \lbrack0,K)$}
	\KwResult{$\Big( E^{N \times L_n}, Y^{N \times L_n} \Big)$ s.t. $E: (((\textrm{typ, } \vec{\textrm{psum}} \textrm{, cnt})_{00}, \dots, (\textrm{typ, } \vec{\textrm{psum}} \textrm{, cnt})_{0L_{0}}),$ \\ $((\textrm{typ, } \vec{\textrm{psum}} \textrm{, cnt})_{0N}, \dots, (\textrm{typ, } \vec{\textrm{psum}} \textrm{, cnt})_{NL_{N}})); Y: \{True, False\}^{N \times L_n}$}
	/* where typ is the object type label, psum is the sum of probabilities for that type within the object region, cnt is the number of pixels in the object region, the training label $Y$ is True if object region is marked, False otherwise, and $L_n$ is total number of objects within image $I_n$ */\;
	\SetKwProg{Def}{def}{:}{}
    \SetKwFunction{N}{Neighbors}
    \Def{\N{x: coord}}{returns Queue of previously marked neighbors to $x$ in ascending order}
	\For{$n \leftarrow 0$ \KwTo $N$}{
    	$\vec{\lambda} \leftarrow \infty^{M}$\;
    	$\lambda_{cur} \leftarrow -1$\;
    	$\vec{\Pi} \leftarrow ()$ // each element points to its parent label\;
    	\For{$m \leftarrow 0$ \KwTo $M$}{
    		$Q \leftarrow$ \N{m}\;
    		\While{$Q \neq \emptyset$}{
    		    $b \leftarrow Q$.pop()\;
    		    $k \leftarrow \argmax_k P_{nm}$\;
    		    \uIf{$k == (\argmax_k P_{nb})$}{
    		        \uIf{$\lambda_b > \lambda_m$}{
    		            $\pi_b \leftarrow \lambda_m$ // record $\lambda_m$ as parent of $\lambda_b$\;
    		        }
    		        \uElse{
    		            $\lambda_m \leftarrow \lambda_b$ // adopt neighbor's label\;
    		            $E_{n\lambda_{m}}$.psum $+= P_{nm}$\;
    		            $E_{n\lambda_{m}}$.cnt $+= 1$\;
    		            \uIf{$m \in t_n$}{$Y_{n\lambda_{m}} \leftarrow True$ // if this is training data}
    		        }
    		    }
    		}
    		\uIf{$\lambda_m == \infty$}{
    		    $\lambda_{cur} \leftarrow \lambda_{cur} + 1$\;
    		    k $\leftarrow \argmax_k P_{nm}$\;
    		    $\lambda_m \leftarrow \lambda_{cur}$\;
    		    $E_n$.append(typ, $P_{nm}$, 1)\;
    		    $Y_n$.append($m \in t_n$) // if this is training data\;
    		    $\Pi$.append($-1$)\;
    	    }
    	}
    	\For{$l \leftarrow (\left| E_n \right| -1)$ \KwTo $0$}{
    	    \uIf{$\pi_l \geq 0$}{
    	        // collapse children into parents\;
    	        $E_{n\pi_{l}} \leftarrow (E_{n\pi_{l}}\textrm{.type}, E_{n\pi_{l}}\textrm{.psum} + E_{nl}\textrm{.psum}, E_{n\pi_{l}}\textrm{.cnt} + E_{nl}\textrm{.cnt})$\;
    	        $Y_{n\pi_{l}} \leftarrow Y_{n\pi_{l}} \textrm{ OR } Y_{nl}$\;
    	        $E_n$.remove($l$); $Y_n$.remove($l$)\;
    	    }
    	}
	}
	return $E$\;
\end{algorithm}

@@

\begin{algorithm}[h!]\label{alg:private}
	\KwData{$E^{N}$ // the enumerated object vectors}
	\KwResult{$P^K$ // probability distribution $p(o \textrm{ is priv})$}
	$C: ((t_0, p_0), \dots, (t_K, p_K)) \leftarrow (0,0)^K$ // total and private counts for each object type\;
	\For{$n \leftarrow 0$ \KwTo $N$}{
	    \For{$l \leftarrow 0$ \KwTo $\left| E_n \right|$}{
	        $k \leftarrow E_{nl}$.typ\;
	        $C_{k}.t += 1$\;
	        \uIf{$E_{nl}$.priv}{$C_{k}.p += 1$}
	    }
	}
	\For{$k \leftarrow 0$ \KwTo $K$}{
	    $P_k \leftarrow C_k.p / C_k.t$\;
	}
	return $P$\;
\caption{Object Privacy Prior Estimate, $O(NL  K)$}
\end{algorithm}

@@

\begin{align}
    p(C_{P_{nm}} = 1 \mid I, \textrm{ evidence}) = \sum_{k=0}^{K} p(i_{nm} \textrm{ on } o_k \mid I_n) P_k
\end{align}

@@

>>>>

\begin{enumerate}
    \item Both tasks are semi-supervised, such that the only form of labeled data is $t_n$\footnote{The semi-supervised assumption was adopted because human point-and-click labeling of private image regions for both training and updating of models is thought to be a realistic scenario.}.  Note that this assumption implies that $t_n$ will not be available at test time.
\end{enumerate}

@@

The objective for this task can be stated as estimating $\{\forall m \in \lbrack0,M), p(C_{P_{m}} = 1 \mid I, \textrm{ evidence}) \}$ where $C_{P_m}$ is the binary class label for whether a pixel $i_m$ is part of a benign object/region (0) or part of a private object/region (1).  This set or probabilities can be regarded as a `privacy map' of $I$ for use in sensorship, for example.

@@

To form the basis of the probabilistic model, a belief network which juxtaposes our evidence and other random variables into the believed set of dependency assumptions can be created. The dependency assumptions are defined as follows.  Firstly, an image ($I$) is the result of, and therefore depends on, the true object-to-pixel mapping ($i_m$ on $o_k$) that is captured by the camera.  Secondly, the scene type ($S$) prediction is based on, and therefore depends on, the image ($I$).  Lastly, we'll assume for now that image meta-data ($D$) in its raw form doesn't meaningfully contribute to the privacy determination problem.  GPS location and time stamps may be useful for influencing the scene probabilities or accounting for lighting differences in the image for object recognition, but we do not have direct influence over those predictors.  The resulting belief network is shown in Figure \ref{fig:belief}.

\begin{figure}[ht]
\centering
    \begin{tikzpicture}[every node/.style={shape=ellipse, draw}]
    %NODES
    \node (io) {$i_{m}\textrm{ on }o_k$};
    \node (i)  [right = of io] {$I$};
    \node (s) [right = of i] {$S$};
    \node (or) [below = of i] {$o_k$ is private};
    \node (d) [right = of s] {$D$};
    %PATHS
    \path   (io) edge [->] (i);
    \path   (i) edge [->] (s);
    \end{tikzpicture}
    \caption{Belief Network}\label{fig:belief}
    %\medskip
    %\small
\end{figure}

We can use Bayes rule and the chain rule to obtain the conditional joint probability distribution $p(i_m \textrm{ on } o, o \textrm{ is private} \mid I, \textrm{ evidence})$.

@@

Time complexity for all algorithms are given in their respective captions.  $N$ is number of images, $M$ is number of pixels per image, $K$ is number of object types, $L_n$ is number of objects in image $I_n$, $Q$ is the number of neighbors to pixels, and $T$ is number of iterations (for root finding). $T$ and $Q$ are presumed to be small.

Equation \ref{eqn:indep} in the previous section illustrates independence of the events that a specific pixel belongs to a specific object and that object being a private object type.  However, the prior distribution $p(i_m \textrm{ on } o \mid I)$ is still unknown.  Estimation of $p(i_m \textrm{ on } o \mid I)$ can be regarded as a constrained Maximum a Priori (MAP) estimation follows:

\begin{gather}
	\theta : \Big(p(i_m \textrm{ on } o_0), p(i_m \textrm{ on } o_1),
		\dots, p(i_m \textrm{ on } o_K)\Big) \\
	L(\theta) = \prod_{n=0}^{N} \sum_{k=0}^{K} p(I_n \mid i_{nm} 
		\textrm{ on } o_k) \theta_k \\
	LL(\theta) = \sum_{n=0}^{N} \log \Big( \sum_{k=0}^{K} 
		p(I_n \mid i_{nm} \textrm{ on } o_k) \theta_k \Big) \label{eqn:loglik}\\
	1 - \sum_{k=0}^{K} \theta_k = 0 \label{eqn:constr}\\
	\mathcal{L}(\theta, \lambda) = \sum_{n=0}^{N} \log 
		\Big( \sum_{k=0}^{K} p(I_n \mid i_{nm} \textrm{ on } o_k) \theta_k \Big) - \lambda + \lambda \sum_{k=0}^{K} \theta_k \label{eqn:lagr}\\
	\mathbf{F}^{K \times 1}: \mathbf{F}_k = \frac{\partial \mathcal{L}}{\partial \theta_k} = 
		\sum_{n=0}^{N} \frac
			{p(I_n \mid i_{nm \textrm{ on } o_k})}
			{\sum_{j=0}^{K} p(I_n \mid i_{nm \textrm{ on } o_j}) \theta_j} 
			    + \lambda = 0;
		\frac{\partial \mathcal{L}}{\partial \lambda} = 1 - \sum_{k=0}^{K} 
			\theta_k = 0 \label{eqn:lagr1der}\\
	\mathbf{J}^{K \times K}: \mathbf{J}_{i,j} = \frac{\partial}{\partial \theta_j}     \left( \frac
		    {\partial \mathcal{L}}{\partial \theta_i} \right) = 
		\sum_{n=0}^{N} \frac
			{-p(I_n \mid i_{nm \textrm{ on } o_i})p(I_n \mid i_{nm 
			    \textrm{ on } o_j})}
			{(\sum_{l=0}^{K} p(I_n \mid i_{nm \textrm{ on } o_l}) \theta_l)^2} \label{eqn:lagr2der};
		%\frac{\partial}{\partial \lambda} \left( \frac{\partial \mathcal{L}}{\partial \lambda} \right) = 0
\end{gather}

Equation \ref{eqn:loglik} represents the Log Likelihood of the observed data to be maximized over $\theta$, and Equation \ref{eqn:constr} represents the constraint that prior probabilities for all object types sum to 1.  A Lagrangian (Equation \ref{eqn:lagr}) is constructed to define the boundary on the Log Likelihood along which the constraint is satisfied.  The roots of the vector of first derivatives for this boundary (Equation \ref{eqn:lagr1der}) will contain the prior distribution that maximizes the posterior distribution.  Equation \ref{eqn:lagr1der} is difficult to solve in closed form. Thus, we will use the Newton-Raphson root finding algorithm to estimate the roots in $O(M(NK + K^3 + TNK))$ time, Algorithm \ref{alg:newtraph}.  This algorithm also requires the second derivative of the Lagrangian, a Jacobian matrix, expressed in Equation \ref{eqn:lagr2der}.

\begin{algorithm}[htp!]\label{alg:newtraph}
\caption{Newton-Raphson Root Finding Algorithm, $O(M(NK + K^3 + TNK))$}
	\KwData{
		$X \leftarrow p(I_n \mid i_{nm} \textrm{ on } o_k)$}
	\KwResult{$\theta^{M \times K}: \{\vec{\theta}_{0}^K, \dots, \vec{\theta}_{M}^K\}$}
	$\theta \leftarrow 0^{M \times K}$\;
	$\alpha \leftarrow$ small constant; $T \leftarrow$ small constant\;
	\For{$m \leftarrow 0$ \KwTo $M$}{
		\For{$n \leftarrow 0$ \KwTo $N$}{
			$\vec{\theta_{m}} \leftarrow \vec{\theta_{m}} + 
				\frac{\vec{p(I_n \mid i_{nm} \textrm{ on } o)}}{N \times \sum_{k=0}^{K} p(I_n \mid i_{nm} \textrm{ on } o_k)}$
				// initial guess for $\theta_{m}$ assuming $I$ is uniform\;
		}
		Build $\mathbf{F}$ // Equation \ref{eqn:lagr1der} complexity $O(NK)$\;
		Build $\mathbf{J}^{-1}$ // Inverse matrix of Equation \ref{eqn:lagr2der} complexity $O(NK+K^3)$\;
		$t \leftarrow 0$\;
		\While{$\mathbf{F}(\theta_{m}) > \alpha$ and $t < T$}{
			$\vec{\theta_m} \leftarrow \vec{\theta_m} - 
				\mathbf{J}(\vec{\theta_m})^{-1} \mathbf{F}(\vec{\theta_m})$
				// complexity $O(NK)$\;
			$t \leftarrow t + 1$\;
		}
	$\vec{\theta_m} \leftarrow \vec{\theta_m} / sum_{k=0}^{K} \theta_{mk}$
		// satisfy constraint (i.e. solve for $\lambda$)\;
	}
\end{algorithm}

@@

However, $p(i_m \textrm{ on } o \mid I)$ is still based on noisy evidence $p(I \mid i_m \textrm{ on } o)$, which has a high potential for resulting in a falsely high number of contiguous object regions.  Aside from the affect of identifying only small portions of private objects, this will also adversely affect $p(o_k \textrm{ is priv})$ by driving up the number of unmarked private objects and potentially mislabeling those that are marked.  Efficient belief propagation over pixels arranged as Markov Random Fields (MRF) has been shown to produce good results in scenarios where labels are unlikely to change between two neighboring pixels except in border regions \cite{felzenszwalb2006efficient}.  We use a variant of this approach to help regularize the noisy $p(i_m \textrm{ on } o \mid I)$ evidence to achieve $p_R(i_m \textrm{ on } o \mid I)$, as shown in Algorithm \ref{alg:regObjMap}.

\begin{algorithm}[htp!]\label{alg:regObjMap}
\caption{Regularize the Object Map, $O(NTMQ^2K)$}
\KwData{
    $I: \{i_{mh} \mid \forall m \in \lbrack 0, M ), \forall h \in \lbrack 0, H)\}$}
\KwResult{$p_R(i_m \textrm{ on } o \mid I)$}
$T \leftarrow$ small number // number of iterations for message updates\;
$d \leftarrow$ small positive constant // penalty for labeling variation\;
$D^{M \times K} \leftarrow -log(p(i_m \textrm{ on } o \mid I))$ /* get object probability map from noisy evidence and convert values to negative log */\;
MSG$^t \leftarrow 0^{M \times \lvert m\textrm{'s neighbors} \rvert \times K}$\;
MSG$^{t-1}$\;
PMAP $\leftarrow$ null$^{M \times K}$\;
\SetKwFunction{h}{h}
\SetKwProg{Def}{def}{:}{}
\Def{\h{x: coord}}{
    res $\leftarrow 0^K$\;
    \For{$k \leftarrow 0$ \KwTo $K$}{
        \For{$q \in$ Neighbors($x$)}{
            $res_k \leftarrow res_k +$ MSG$^{t-1}_{q,x,k}$\;
        }
        $res_k \leftarrow res_k + D_{x,k}$\;
    }
    return $res$
}
\SetKwFunction{Nei}{Neighbors}
\Def{\Nei{x}}{return 8 pixel coordinates around x // could be 4\;}
\For{$t \leftarrow 0$ \KwTo $T$}{
    // Update messages $T$ times\;
    MSG$^{t-1} \leftarrow$ MSG$^t$\;
    \For{$m \leftarrow 0$ \KwTo $M$}{
        // for each pixel coordinate\;
        $h_m \leftarrow$ \h{$m$}\;
        $h_{m_{min}} \leftarrow \min_{k} (h_m + d)$\;
        $Q \leftarrow$ Neighbors($m$)\;
        \For{$q \in Q$}{
            $h_q \leftarrow$ \h{$q$}\;
            \For{$k \leftarrow 0$ \KwTo $K$}{
                MSG$^t_{m,q,k} \leftarrow \min (h_{q_{k}}, h_{m_{min}})$
            }
        }
    }
}
\For{$m \leftarrow 0$ \KwTo $M$}{
    $p_R(i_m \textrm{ on } o \mid I) \leftarrow \frac
	    {\vec{log^{-1}(-\textrm{\h{m}})}}
	    {\sum_{k=0}^{K}log^{-1}(-\textrm{\h{m}})}$
	    // conv. to probability and ensure normalized\;
}
return res\;
\end{algorithm}

The final task is to estimate $p(o \textrm{ is priv})$.  To achieve this, we need to enumerate all the object instances, their types, their respective probabilities, and whether they are private.  To achieve this, we us a variant of the Two-Pass Connected Component Labeling algorithm \cite{hoshen1976percolation}, described in Algorithm \ref{alg:objEnum}.  It is important to note that although objects are enumerated according to the highest object type probabilities for each pixel, probability summations for all objects types are preserved at each pixel.  This will be important later.

\begin{algorithm}[htp!]\label{alg:objEnum}
\caption{Object Enumeration, $O(NMQ + L)$}
	\KwData{$P^{N \times M \times K} \leftarrow p_R(i_{nm} \textrm{ on } o_k \mid I_n) \forall n \in \lbrack 0,N), \forall m \in \lbrack0,M), \forall k \in \lbrack0,K)$}
	\KwResult{$\Big( E^{N \times L_n}, Y^{N \times L_n} \Big)$ s.t. $E: (((\textrm{typ, } \vec{\textrm{psum}} \textrm{, cnt})_{00}, \dots, (\textrm{typ, } \vec{\textrm{psum}} \textrm{, cnt})_{0L_{0}}),$ \\ $((\textrm{typ, } \vec{\textrm{psum}} \textrm{, cnt})_{0N}, \dots, (\textrm{typ, } \vec{\textrm{psum}} \textrm{, cnt})_{NL_{N}})); Y: \{True, False\}^{N \times L_n}$}
	/* where typ is the object type label, psum is the sum of probabilities for that type within the object region, cnt is the number of pixels in the object region, the training label $Y$ is True if object region is marked, False otherwise, and $L_n$ is total number of objects within image $I_n$ */\;
	\SetKwProg{Def}{def}{:}{}
    \SetKwFunction{N}{Neighbors}
    \Def{\N{x: coord}}{returns Queue of previously marked neighbors to $x$ in ascending order}
	\For{$n \leftarrow 0$ \KwTo $N$}{
    	$\vec{\lambda} \leftarrow \infty^{M}$\;
    	$\lambda_{cur} \leftarrow -1$\;
    	$\vec{\Pi} \leftarrow ()$ // each element points to its parent label\;
    	\For{$m \leftarrow 0$ \KwTo $M$}{
    		$Q \leftarrow$ \N{m}\;
    		\While{$Q \neq \emptyset$}{
    		    $b \leftarrow Q$.pop()\;
    		    $k \leftarrow \argmax_k P_{nm}$\;
    		    \uIf{$k == (\argmax_k P_{nb})$}{
    		        \uIf{$\lambda_b > \lambda_m$}{
    		            $\pi_b \leftarrow \lambda_m$ // record $\lambda_m$ as parent of $\lambda_b$\;
    		        }
    		        \uElse{
    		            $\lambda_m \leftarrow \lambda_b$ // adopt neighbor's label\;
    		            $E_{n\lambda_{m}}$.psum $+= P_{nm}$\;
    		            $E_{n\lambda_{m}}$.cnt $+= 1$\;
    		            \uIf{$m \in t_n$}{$Y_{n\lambda_{m}} \leftarrow True$ // if this is training data}
    		        }
    		    }
    		}
    		\uIf{$\lambda_m == \infty$}{
    		    $\lambda_{cur} \leftarrow \lambda_{cur} + 1$\;
    		    k $\leftarrow \argmax_k P_{nm}$\;
    		    $\lambda_m \leftarrow \lambda_{cur}$\;
    		    $E_n$.append(typ, $P_{nm}$, 1)\;
    		    $Y_n$.append($m \in t_n$) // if this is training data\;
    		    $\Pi$.append($-1$)\;
    	    }
    	}
    	\For{$l \leftarrow (\left| E_n \right| -1)$ \KwTo $0$}{
    	    \uIf{$\pi_l \geq 0$}{
    	        // collapse children into parents\;
    	        $E_{n\pi_{l}} \leftarrow (E_{n\pi_{l}}\textrm{.type}, E_{n\pi_{l}}\textrm{.psum} + E_{nl}\textrm{.psum}, E_{n\pi_{l}}\textrm{.cnt} + E_{nl}\textrm{.cnt})$\;
    	        $Y_{n\pi_{l}} \leftarrow Y_{n\pi_{l}} \textrm{ OR } Y_{nl}$\;
    	        $E_n$.remove($l$); $Y_n$.remove($l$)\;
    	    }
    	}
	}
	return $E$\;
\end{algorithm}

@@

\begin{algorithm}[htp!]\label{alg:private}
	\KwData{$E^{N}$ // the enumerated object vectors}
	\KwResult{$P^K$ // probability distribution $p(o \textrm{ is priv})$}
	$C: ((t_0, p_0), \dots, (t_K, p_K)) \leftarrow (0,0)^K$ // total and private counts for each object type\;
	\For{$n \leftarrow 0$ \KwTo $N$}{
	    \For{$l \leftarrow 0$ \KwTo $\left| E_n \right|$}{
	        $k \leftarrow E_{nl}$.typ\;
	        $C_{k}.t += 1$\;
	        \uIf{$E_{nl}$.priv}{$C_{k}.p += 1$}
	    }
	}
	\For{$k \leftarrow 0$ \KwTo $K$}{
	    $P_k \leftarrow C_k.p / C_k.t$\;
	}
	return $P$\;
\caption{Object Privacy Prior Estimate, $O(NL  K)$}
\end{algorithm}

@@

\begin{align}
    p(C_{P_{nm}} = 1 \mid I, \textrm{ evidence}) = \sum_{k=0}^{K} p_R(i_{nm} \textrm{ on } o_k \mid I_n) P_k
\end{align}

In summary, we can estimate $p(i_m \textrm{ on } o)$ once in $O(M(NK + K^3 + TNK))$ time, regularize $p(i_m \textrm{ on } o \mid I)$ for all images in $O(NTMQ^2K)$ time, enumerate the objects in all images in $O(NMQ + L_n)$  time, estimate $p(o \textrm{ is priv})$ once in $O(N L_n K)$ time, and finally estimate the pixel privacy probability for all images in $O(N M K)$ time.  Since $L_n < M$, total running time for estimating all pixels for all images is $O(MK^3 + NMTKQ^2)$ where $T$ and $Q$ are presumed to be small.

@@

\textit{Important note.}  A qualifying exam tests your technical
knowledge and abilities, but also your potential to conduct
independent, high-quality research using  the highest ethical standards.
In answering the question below, you may consult existing
published work, but you may not discuss the question with people other than
members of the advisory committee.  (The sole exception is that you
may seek non-technical help with English from the writing center on
campus, but then you must submit both your original draft as well as
the final draft after incorporating feedback from the editor or
writing center.)  The University's academic integrity policy will
govern this exam. In particular, all material you submit
must be your own work which you
personally and independently completed. If any portion of your
submitted material is not your own work, you must make this explicitly
clear using proper citations. For instance, all sentences in your
report must be your own unless you place the relevant sentences in
quotation marks and give a citation to the source.  \textit{Note that
  descriptions and discussions of existing work are to be in your own
  words based on your understanding of the work; it is \textbf{not}
  acceptable to copy or paraphrase even a small part of another work
  unless it is placed inside quotation marks and properly cited.}
{In accordance with University policy, consequences of academic
  integrity violations  include failure on this exam and expulsion
  from the University.}
